{\LARGE \textsc{Biotic invasions reduce the manageability of mutualistic networks}}

### 2016-05-11 paper/manuscript.Rnw
start working on the introduction

\textit{Tentative spiel for the first paragraph:} We need to manage ecological communities because of ecosystem services and biodiversity maintenance. We would like to control communities in the sense of conserving and restoring them. However to control them (in that sense) we need to understand how species affect each other and potentially the whole system when they are faced by perturbations or management interventions. But we cannot do that yet because we lack a theoretical framework that link the dynamics of the community to management. Control theory might provide this link.

In contrast with other types of complex systems like neural, intra-organizational, or trust neworks, ecological networks do not have a hierarchical or distributed structure but rather tend to be closed systems in which resources recirculate\todo{add ref}. As such, ecosystems contain multiple feedbacks that allow them to self-regulate and, therefore, function relatively independent from external stimulation\todo{add ref}.

Research stemming from control theory has established a strong link between the structure of complex networks and their controlability and that, in principle it is possible to alter a ecological community's composition by modifying the abundances of only a few species \autocite{Liu2011, Cornelius2013}. Based on this work and using a small number of binary food-webs (only presence or absence of interactions), it has been suggested that the degree distribution of ecological networks makes them inherently difficult to control \autocite{Liu2011, Ruths2014}. This theoretical result is in agreement with many cases in which the management of ecological communities is more challenging than aticipated.  Although these conceptual advances on control theory have provided an initial link between the structure of ecological communities and our ability to manage them, this relationship is still ambiguous. Ultimately, the challenge of ecological networks is represented by the variablity of their structure and interaction strengths---which can vary by several orders of mangitude\todo{add ref}.

>>>>

\textit{Tentative spiel for the first paragraph:} We need to manage ecological communities because of ecosystem services and biodiversity maintenance. We would like to control communities in the sense of conserving and restoring them.

However to control them (in that sense) we need to understand how species affect each other and potentially the whole system when they are faced by perturbations or management interventions.

But we cannot do that yet because we lack a theoretical framework that link the dynamics of the community to management. Control theory might provide this link.

 This idea hasboth helped and hindered the search for solutions to many problems facing said communities today. On the positive side, for example, it has led to the development of a rich suite of analytical and simulation tools with which to blah blah, even though ecology has not historically been a highly quantitative field. On the negative side, this complexity is often thought to be so rampant that attempts to explain, predict, or manage community dynamics will always fall short of the mark. Blah, blah, blah....

Complex systems, like ecological communities, are characterised by non-linear relationships in which the whole is greater than the sum of its parts \todo{add refs}. This complex systems approach has helped the search for solutions to problems that these communinities face at the same time it has led to the development of a rich suite of analytical and simulation tools with which to understand the role of species when embedded in an intricate network of interactions\todo{add refs}. However, in contrast with other types of complex systems like neural, intra-organizational, or trust neworks, ecological networks do not have a hierarchical or distributed structure but rather tend to be closed systems in which resources recirculate\todo{add ref}. As such, ecosystems contain multiple feedbacks that allow them to self-regulate and, therefore, function relatively independent from external stimulation\todo{add ref}. This property has hindered our ability to effectively explain, predict, or manage the dynamics of ecological communities, particularly when they are faced by perturbations. In part this is because... we lack a theoretical framework that link the dynamics of the community to management. Control theory might provide this link.

because we are still not able to explain, predict how species affect each other and potentially the whole system when they are faced by perturbations.

Research stemming from control theory has established a strong link between the structure of complex networks and their controlability, and that, in principle, it is possible to alter a ecological community's composition by modifying the abundances of only a few species \autocite{Liu2011, Cornelius2013}. Based on this work, it has been suggested that the degree distribution of ecological networks makes them inherently difficult to control \autocite{Liu2011, Ruths2014}. This theoretical result is in agreement with many cases in which the management of ecological communities is more challenging than aticipated.

Although these conceptual advances on control theory have provided an initial link between the structure of ecological communities and our ability to manage them, this relationship is still ambiguous. Ultimately, the challenge of ecological networks is represented by the variablity of their structure and interaction strengths---which can vary by several orders of mangitude\todo{add ref}.
